% !TeX TS-program = LuaLaTeX
% !TeX encoding = UTF-8
\documentclass{novel}
%%% METADATA (FILE DATA):
\SetTitle{TITLE}
\SetAuthor{AUTHOR}
\SetPDFX{X-1a:2001}
\SetTrimSize{4.25in}{6.875in}
\SetMediaSize{4.5in}{7.12in}
\SetMargins{0.5in}{0.5in}{0.5in}{0.7in}
\SetParentFont{Libertinus Serif}
\SetFontSize{9.5pt}
\SetHeadFootStyle{5}
\SetHeadJump{1.5}
\SetFootJump{1.5}
\SetLooseHead{50}
\SetEmblems{}{} % Default blanks.
\SetHeadFont[\parentfontfeatures,Letters=SmallCaps,Scale=0.92]{\parentfontname}
\SetPageNumberStyle{\thepage}
\SetVersoHeadText{\theAuthor}
\SetRectoHeadText{\theTitle}
%%% CHAPTERS:
\SetChapterStartStyle{footer} % Equivalent to empty, when style has no footer.
\SetChapterStartHeight{10}
\SetChapterFont[Numbers=Lining,Scale=1.6]{\parentfontname}
\SetSubchFont[Numbers=Lining,Scale=1.2]{\parentfontname}
\SetScenebreakIndent{false}
%%% BEGIN DOCUMENT:
\begin{document}
\frontmatter
\thispagestyle{empty}
% Half-Title Page.
\begin{parascale}[2]
\vspace*{3\nbs}
\centering\charscale[0.75]{TITLE }\par
\centering\charscale[0.75]{TITLE LINE 2}\par
\centering{TITLE LINE 3}\par
\end{parascale}
\clearpage
\thispagestyle{empty}
\null % Necessary for blank page.
% Alternatively, List of Books.
\clearpage
\thispagestyle{empty}
% Title Page.
\begin{parascale}[4]
\centering\charscale[0.75]{TITLE }\par
\centering\charscale[0.75]{TITLE LINE 2}\par
\centering{TITLE LINE 3}\par
\end{parascale}
\vspace*{2\nbs}

\begin{parascale}[1]
\centering\textit{SERIES}\par
\vspace*{3\nbs}
\charscale[2]{AUTHOR}\par
\end{parascale}
\vfill
\begin{parascale}[1]
% \centering\InlineImage[0, 3em]{/home/darkstar/dox/working-files/LaTeX/atticus.jpg}

A Tales of Murder Press, LLC\par
\textit{GENRE} Novel\par
\end{parascale}
\clearpage
\thispagestyle{empty}
% Copyright Page.
\null\vfill
\allsmcp{First edition} PUBLICATION_DATE\par
\null\null
\allsmcp{ISBN}\par
\null\null
\vfill
\begin{adjustwidth}{3em}{3em}
\textit{This novel is in the public domain.} Certain \mbox{elements} in this edition are Copyright © COPYRIGHT_DATE Tales of Murder Press, LLC
\end{adjustwidth}
\clearpage
\thispagestyle{empty}
\clearpage % because ToC must start recto
\thispagestyle{empty}
\begin{toc}[0.5]{0em}
{\centering\charscale[1.25]{Contents}\par}
\null

%some kind of loop through chapters for TOC
\tocitem*[1]{CHAPTER_TITLE}{STARTING_PAGE}
\end{toc}
%end loop
\clearpage

\mainmatter
\cleartorecto
\thispagestyle{empty}

%some kind of loop through all chapters
\begin{ChapterStart}
\vspace{3\nbs}
\ChapterSubtitle[l]{Chapter 17}
\ChapterTitle[l]{## Pursuit of an Equation}
\end{ChapterStart}
\FirstLine{\noindent ### Chapter 17

## Pursuit of an Equation

That week there were three more floating games in hotel rooms. I did very well in one and fair in the two others. But I got nowhere at all in the real purpose behind my playing. I saw Don Yard only at the pay-offs and then briefly. Tackling Walter, I had learned, was a waste of breath, if not hazardous. Bertha Kaleman seemed to be my best bet, but I couldn’t get her off by herself. Twice I phoned the unlisted number to ask her out to lunch. The first time there was no answer. The second time I hung up as soon as I heard Yard’s voice over the wire.

On a Tuesday, two weeks after I hit New York, I accepted Earl Locust’s invitation to take part in one of the murderous table stakes draw games he held in his study. Yard and Walter wouldn’t be there; they were busy on another project of theirs I knew nothing about. This was extra-curricular, winning or losing my own money. As it turned out, losing.

The game was an hour old when Robin Magee came in.

I suppose it was inevitable. If not Magee, it would have been somebody else. New York is immense, but even an out-of-towner like myself was always bumping into acquaintances. I tried to protect myself by keeping off the street as much as possible and depend on taxis for transportation. And now here was Robin Magee regarding me with that silky smile of his.

Locust rose from the table and introduced him to two players Magee had not met before. Then it was my turn. “Mac, I want you to meet Jeff Barcowitz who took us to the cleaners last game we had up here. He plays a mean poker. Jeff, shake hands with Robin Magee, the noted criminal lawyer.”

We shook hands. I doubt if there was any blood in mine. We looked into each other’s eyes. Magee broadened his smile and sat down beside me. The game resumed.

I’d been due for a streak of bad cards. It had started before Magee’s arrival, and the fact that he was now sitting beside me didn’t help my playing. I tightened up, supporting only cinches, and was lucky to get away with a loss of only a couple of thousand dollars. Or a couple of grand, as I was beginning to think of such an amount.

***

When the game ended, Magee and I left together. We walked a full block in the early morning quiet before either of us spoke. Then Magee chuckled.

“Berkowitz! That’s a little masterpiece. Who would think of Alexander Linn as Berkowitz, or the other way around?”

“What do you propose to do about it?” I said.

The chuckle died. He stopped walking and I stopped and we stood against a wall, two shadows; beyond the sickly rim of the nearest street light.

“I’m in a difficult position, my boy,” he said somberly. “My clients would lose confidence in me if I were to turn a former client of mine over to the police. Though you are wanted for an entirely different murder than the one for which I defended you, the fact remains that I was recently consulted concerning this second case.”

“By George Winkler?”

“He came to my office last week with Miriam Hennessey.”

“How is she?”

“Not well. Winkler told me later that she is eating her heart away. I feel sorry for that poor girl. A hardened cynic like me cannot understand why women are always falling irrevocably in love with the men who hurt them most.”

A milk wagon cluttered leisurely by. The horse appeared to be asleep on its feet.

“Miriam doesn’t love me like that,” I muttered.

“My boy, you are as blind as a bat if you really think that. It was plain to me in every word she said. Later, when I had a private talk, with Winkler, he said that if you had had an iota of sense you would have married Miriam in the first place and avoided all this trouble.”

The milk wagon turned into Third Avenue. The street was empty now except for the two of us standing against the wall.

“I suppose there’s no use telling you I didn’t kill Schneider,” I said.

He shrugged his aristocratically stooped shoulders. “I am a defense attorney, not a prosecutor or a juror. Winkler and Miriam came to New York to consult me as to your chances if you were caught or gave yourself up. Frankly, I would not give one chance in ten to your being acquitted this time. I believe, however, that I can get you committed to an institution.”

“I prefer the chair to a nuthouse!“

“Then you’ll get it.”

“I’m not giving myself up,” I said fiercely. “I’m fighting.”

He looked searchingly at me, though he could not see more than an outline of my face. “They tell me you are an intelligent young man, but you haven’t impressed me as such. Not before and during your trial and; certainly not now. Is this a rational way to hide out, going about openly in New York and participating in big poker games when the police are aware of your reputation as a poker player?”

“I’m looking for the murderer.”

“In New York?”

***

Evidently Locust hadn’t told him that I’d met Don Yard through him, and probably nobody but Walter and Bertha knew that I was working for Yard. Let him keep thinking that I was playing poker as the only way I had to make a living while in hiding.

“I’m working on an equation,” I muttered. “Some of the terms might be found here?”

“Terms?”

“For the hypotheses of a linear equation which I hope will tell me who murdered Lily and Schneider. Of course it can’t be strictly mathematical. There can’t be fixed values. But if I can find the right terms and then satisfy the equation—”

Magee said: “I’m sure that I can persuade a jury to find you psychologically irresponsible. This time we’ll bring in experts to testify.”

What I’d said about equation hadn’t gone through his ears. I was a crackpot raving wildly, a psychoneurotic in an advanced stage. We were back where we’d started from weeks ago. There was no common meeting ground, nothing I could say which he would understand or believe.

“Look,” I said. “I’m going to start walking away from here. Will I have to worry about the police coming after me?”

For a long minute he was a motionless and silent shadow against the wall. Then he said: “I cannot afford to be known as an attorney who hands his clients over to the police. I can only urgently advise you to give yourself up. There are ways of getting you out of a mental institution after a period of time.”

Everything emptied out of me. For the first time it struck me that he and all the others could be right. I was mad and had murdered two people without remembering. Or not a murderer and not completely insane, but sufficiently cracked to stake my life on an equation which was not mathematics or psychology or anything else in the books.

“I’ll be glad to accompany you to a police station,” Magee said gently.

I turned and walked away from him. In the breaking dawn I found myself at the East River. I turned back to the west. Men and women were leaving for work when I climbed the stoop of Mrs. Egan’s rooming house.

***

In the winter we needed blankets and moved in from the front porch and its protecting canopy to one of the three rooms into which our hut was divided. But the straw ticks continued to smell of mold and there were the little indefinable sounds which might be a scorpion crawling into your boots or a snake slithering inside or outside the wall. Just before sundown Kassim, my bearer, had bashed in the head of a deadly krait which had been within a yard of my leg. He had grinned delightedly as he had held it up by its tail. “Bas!” he had said. Finished! Meaning not the snake, but me if he, Kassim, hadn’t been quick enough.

I kicked the blanket off me. Winter or summer, India was no place for sleeping. I turned on my side, and there was a woman in bed with me. I smiled. This was what I had needed all along. I stretched out a hand to her. It froze in horror. Her hair consisted of peculiarly colorless kraits squirming toward me. The woman looked along her white passionate body and laughed at my terror. And her face was Lily’s face.

I tried to roll off the bed, but I could not move. Medusa turned her victims to stone. I lay with eyes closed on the damp sheet, waiting for Lily to dip her head closer and let the snakes get their venom into me. I heard her stir. I felt her hot flesh along my arm as she bent lower to bring the snakes into range. I screamed soundlessly and with a vast effort twisted my head to her.

The snakes were gone. Her hair was hair now, but it was not the platinum of Lily’s hair. It was black and very long and it lay spread over burnished tan flesh without quite covering it. Intense black eyes searched my face. The wide mouth was partly open—a mouth to be kissed.

“Miriam!” I cried joyfully.

There would be no snakes in Miriam’s hair, nothing to hurt me. I reached out my arms for her, and suddenly I was alone, tossing in my bed in Mrs. Egan’s rooming house. The sheet under me was damp. A high, hot sun poured in through the window and over my face and body.

My watch said two-thirty. It was afternoon, but I hadn’t slept enough. It was a long time since sleep had rested me. I turned my face away from the sun and closed my heavy lids.

***

There was a knock on the door.

I got out of bed, rubbed my eyes with my knuckles and then scratched my back. The knock was repeated. I went to the door and asked who it was. “Bertha.”

“Who?” I said stupidly.

“Bertha Kaleman. Is there any reason why I can’t be invited in?”

I turned the key and started to turn the knob before I realized that I wasn’t in proper attire to receive sleekly turned out female company. “Wait a minute,” I said. “I’m not dressed.”

The unlocked door was opening. “I don’t mind,” she said and came all the way in. She looked me over. “Why the fuss? You’re wearing pajamas.”

“It covers more than a sheer yellow nightgown with ‘Forget Me Not,’ embroidered on the bosom,” I said.

“I see you haven’t forgotten.”

“Do you think I could?”

She patted my face with a white-gloved hand. “You’re cute, Berky. No wonder I’ve fallen for you.”

I didn’t say anything. She strolled by me to the dresser. Her hat was built like a layer cake, the bottom layer black and the top and smaller one royal blue. Her black dress was also in tiers, the material folding out from her adequate hips and twice again before the hem. At the slashed bosom there was another tier, but that wasn’t the design of the dress. That was Bertha.

“Aren’t you glad to see me, Berky?” she said into the dresser mirror. She was removing the layer cake gingerly to preserve the complicated hairdo.

“It might be a prudish upbringing, but I was taught to entertain women with my clothes on, at least in the early stages.”

She smiled brightly into the mirror. I gathered up my clothes and carried them into the bathroom.

When I came out, her handbag and gloves were beside the layer cake on the dresser. She stood at the window, looking down into Eighty-Second Street. I went to her side.

“Sorry I and the room are such a mess,” I said. “I wasn’t prepared for company.”

“I dropped in for a moment to ask if you’d like to see a musical tonight. ‘High Feathers.’ Somebody gave Don four tickets. He was going to give two to Walt, but Walt has no girl friends, so I suggested that we take you. Don said all right.”

“And he sent you up here to tell me?”

“I imagine he assumed I’d phone you.”

“But you didn’t. You came in person.”

This time the hand was placed on my chest. The full, painted mouth was surprisingly close. I didn’t know it was going to be a kiss until it was an accomplished fact. Her hands slid up under my armpits. I held her tight. She felt very good. After a while I found myself looking at the artificial lashes at the edge of exotically darkened eyelids, and I told myself that I mustn’t like it too much. I must use it, but not let it run away with me.

***

I took my mouth and the rest of me away from her and went to the dresser and lighted a cigarette. Through the mirror I saw her undulate after me. The cigarette was plucked from my fingers. She brought it to where a smear of lipstick ruined the corner of her mouth.

“What’s the matter, Berky?” she said mockingly. “Didn’t you enjoy it?”

“I’m scared of Don,” I told her. “I don’t claim to be as tough as Walter, and he was scared sick last week when he thought you might tell Don that he’d forced himself on you.”

“You’re taking a big jump ahead. What do you think is going to follow that kiss?”

“I can hope, can’t I?” I sat down on the edge of the unmade bed and worked at looking miserable. “What would Don do if you left him for me?”

“You’ll never get a chance to find out. It was a nice kiss. Period. Don’s my man and I’m sticking to him. Don’t forget it.” She turned to the mirror to inspect her face. It needed refurbishing after that kiss. She took stuff out of her handbag.

“You’re safe now,” I said to her back, “with Lily dead.”

The lipstick paused at the corner of the mouth. “What do you mean by that crack?”

“Remember how Don almost took a sock at me when I talked about Lily and the second man she’d married? And Walter warned me to keep my mouth shut about her. Don can’t stand hearing about her. She’s dead, but he’s not got over being in love with her and never will.”

“Don’t try to get profound, Berky,” she said into the mirror.

“Don’s in love with a ghost,” I went on, “yet Walter was afraid of what Don would do to him for making love to you. It isn’t sense.”

She concentrated on restoring the lips. Then she said: “Don holds onto what he has. He has me.”

“And you hold onto what you have,” I said. “Even when Lily was alive she was a ghost haunting you. You were only sitting in for her. Don would have dropped you in a minute if she wanted to go back to him. She had you worried all the time.”

I expected Bertha to flare out and spew out angry words. She didn’t. She was changing a pin in her flame hair and looking at my reflection in the mirror. She only said: “You seem to know a hell of a lot, Berky.”

“I can add two and two.”

“Why all this talk? What’s it supposed to lead to?”

“I have to find out where I stand if you keep coming up to this room. I’m no hero. But if Don let somebody get away with marrying Lily when he still wanted her, why should he get tough with me about you?”

***

Her face was properly lacquered.

She turned and leaned languidly against the dresser, the three tiers of her dress jutting. “Don’s a funny guy,” she said thoughtfully. “He’s a poker player twenty-four hours a day, keeps things to himself. But when he breaks loose, he’s bad. I think that’s what made Lily divorce him. She liked money more than any woman I ever knew and Don has plenty. She liked Don, too. He’s a woman’s man, but never mind that. Lily gave him plenty of reason to get jealous and explode. Perhaps the reason she married that kid Linn in such a hurry was to get away from Don, even after she had the divorce. There’s something in having a legal husband that even Don would be afraid to buck. Yeah, she was scared of him. So is Walter and so are you and so am I. I’m coming up here for a few reasons. One of them is I don’t want to get you into trouble.”

“He didn’t do anything to Linn.”

“Like I said, that was marriage. Me coming up here is cheating on him. Besides, Linn went overseas a few days after he married Lily and didn’t come back till the night he murdered her, so you can’t tell what Don would have done.”

I had maneuvered up to it. I said: “Maybe it was Don who murdered Lily.”

“Two years after she married Linn?”

“It was the night Linn came back to live with Lily,” I said. “Don had been up to see her at a party only the week before. You were there. He must have got her off by himself and asked her again to come back to him. She turned him down. He couldn’t stand the thought of another man coming back to live with her. The next Saturday night he drove up there alone and killed her.”

Her artificial lashes almost covered her eyes. “How do you know so much about what happened?”

“That newspaper article was pretty detailed.”

“There was nothing at all about Don being married to Lily in that local paper he subscribes to. Nothing about me either or that party at Lily’s the week before.”

The air in the room was suddenly stifling. “What local paper?”

“A weekly sheet, the Hale County Star. That’s the upstate county where Lily was murdered. Don subscribed to it because it was the only paper that carried all the details of the murder and the trial. When it came in the mail, he’d spend hours sitting and reading the same words over and over. Then when he read that Alexander Linn was acquitted, I couldn’t talk to him for a whole day. I was; almost afraid he’d go up there and do his own executing, since the law wouldn’t. Maybe he would’ve if Linn hadn’t murdered Schneider only two days later and then taken a powder.”

***

That was why my face had been familiar to her and Yard when they’d met me. Twice within two months they’d seen my photo in the Star—an inaccurate and poorly reproduced halftone which had been like a face vaguely glimpsed in a crowd and remembered without detail. If they had seen my photo after I had come to them, after they had my living features before them, they would have made the connection.

I said: “The writer of the article I read must have scooped the local reporters on Don’s marriage to Lily, and the other dirt.”

That may have satisfied Bertha as to the source of my knowledge. I couldn’t tell. She appeared to have lost interest in the topic. She was facing the mirror and setting the layer cake on her flame hair.

“How can you be sure Don didn’t kill Lily?” I said.

“It’s plain that Linn killed her.”

“He never stopped insisting that he was innocent.”

The hat was precariously in place. She started to draw on her gloves. “Now I see what you’re after, Berky. If you can get Don jailed for murder, you can have me without worrying about him. You’re barking up the wrong tree. First of all, Don wouldn’t have harmed a hair of her head. Maybe he’d kill the guy who married her, but not her. Second, he was on Cape Cod the night she was murdered.”

“Are you sure?”

“I ought to be. I was with him. We drove out there Friday. We were to stay a week or so. Monday morning Walt phoned Don from New York that he’d just read a couple of lines in the morning paper that Lily had been murdered Saturday night. Don drove right back to New York, as if he could do anything about it, and then he called up the Hale County Star, and got the dope about the murder. Her death hit him like a ton of bricks.”

“Where was Walter that Saturday night?”

“How should I know? Somewhere around New York, I guess. Say, don’t tell me you got an idea that Walt killed her?”

“No,” I said. “All right, Don didn’t kill her. He wouldn’t harm her and he was on Cape Cod. But Schneider had been her lover. Maybe Don killed him.”

“Why only Schneider? Why not Linn, and while he was at it, all the others she’d ever messed around with?” She shook her head. “Berky, there’s nothing in it. You’re not going to get Don out of the way like that. Even if I thought you could, I wouldn’t play along. I’d keep my mouth shut.” She picked up her handbag. “I should’ve phoned you instead of coming here.”

I rose from the bed and put my hands on her shoulders and kissed her. It wasn’t like the first one. She broke it up after a couple of seconds.

“You’re a sweet boy, Berky,” she said listlessly, “but you spoiled it by talking too much. Your ticket for the show will be waiting for you at the box office.”

“I can’t make it,” I told her. Broadway and public places were out of bounds for me. I knew hundreds of airmen all over the world, and sooner or later some of those who survived would turn up in New York, which to a man back from action, meant bright lights and nightclubs and theaters.

Her eyes were screened by the artificial lashes which were red to match her hair. “You let a man kiss you and he gets sore at you,” she said. “You can never give a man enough.”

Here was the chance I’d been waiting for, to become socially friendly with the three of them. Bertha had kissed me and Yard had asked me to the theater. The ice was broken. I’d been gambling from the first and taken plenty of risk. Why not a little more? “All right, I’ll be there,” I said.

There was no farewell kiss. My cheek was patted with a gloved hand and then she was gone.

***

A bottle of milk was in the refrigerator. With a glass of it in my hand, I opened the top righthand drawer of the dresser and took out the sheets of yellow paper on which I had written variations of the equation. I pushed aside the embroidered scarf which covered the dresser top and spread out a fresh sheet of paper and wrote:

The following are the possible suspects: Miriam Hennessey, Ursula Hennessey, Kerry Nugent, George Winkler, Oliver Spencer, Bevis Spencer, Helen Spencer, Ogden Gar back, Don Yard, Walter.

I read over the list as I drank down the milk. Then I added, “Owen Dowie,” and under it I wrote:

Which of the suspects will satisfy the linear equation with a single unknown which results from the following hypotheses?

Let X=the Suspect.

Let OL=Opportunity to murder Lily.

Let KL=Knowledge of my movements in Lily’s murder.

Let ML=Motive for murdering Lily.

Let

I left it there and went into the bathroom to shave. I returned to the dresser and picked up my pen. There were eight terms in all. I didn’t finish the summary. I could see which was the only one of the ten X’s the equation could satisfy.

So what did I have? I was using a system of trial and error in a technique which required fixed values. I slammed down the pen. The point broke.

At once I regretted my rage. That pen had served me through college and in the Air Force. Many years ago Miriam had given it to me for a birthday present.



\vspace{2\nbs}
\ChapterDeco[c1]{\decoglyph{e9665}}
\clearpage
\thispagestyle{empty}

%end chapter loop

\scenebreak
\scenebreak
{\centering\textsc{the end}\par}

\clearpage

\null

\centering\textsc{www.TalesofMurder.com}\par

\vspace*{10\nbs}

%\centering\InlineImage[0, 3em]{/home/darkstar/dox/working-files/LaTeX/atticus.jpg}

TALES OF MURDER PRESS, LLC

\null

\scshape{675 TOWN CENTER BLVD
BLDG 1A STE 200 PMB 530
GARLAND, TEXAS 75040}

\null

\textit{atticus@talesofmurder.com}
\vfill


\end{document}

